\documentclass[12pt,a4paper]{article} 

\title{\bf Dual MLP Pairs with Hidden Layer Sharing}

\author{Ivan Blagoev, Janeta Sevova, Kolyu Kolev \\
Institute of Information and Communication Technologies \\
Bulgarian Academy of Sciences \\
acad. Georgi Bonchev Str, block 2, 1113 Sofia, Bulgaria \\
i.blagoev@iit.bas.bg \\
http://www.iict.bas.bg/}

% Ivan Blagoev i.blagoev@iit.bas.bg
% Janeta Sevova janetasevova@gmail.com
% Kolyu Kolev kolev_kolyu@yahoo.com

\date{}

\begin{document}

\maketitle

Artificial neural networks are well known and widely used from decades. One of the most popular kinds in the multilayer perceptron (MLP). Its general characteristic is that it has more than one layer. The most used topology of MLP has three layers (input, hidden and output). Layers are fully-connected between each other (the input with the hidden and the hidden with the output). The general disadvantage of this topology is that it does not has recurrent connections. Also the common usage of MLP is for single task solving. This research addresses these two common features of the MLP. Two MLPs are modified in such way that they share common hidden layer. Both MPLs have the task to forecast currency values (EUR/USD for the first one and USD/JPY for the second one). The lack of recurrent connections is solved by pairing each of the MLPs with another two MPLs. Pairs are done in such way that the output of the single MPL is take as input for its pairing MPL and the output of the pairing MPL is supplied at the original input. By such structure of four MPLs knowledge transfer is achieved by the shared hidden layer and short term memory is presented by the pairs. 

\end{document}