\documentclass[12pt,a4paper]{article} 

\title{\bf Blockchain Solution for Annual Evaluation into Bulgarian Schools}

\author{Delyan Keremedchiev, Todor Balabanov \\
Institute of Information and Communication Technologies \\
Bulgarian Academy of Sciences \\
acad. Georgi Bonchev Str, block 2, 1113 Sofia, Bulgaria \\
d\_keremedchiev@bas.bg \\
http://www.iict.bas.bg/}

% Delyan Keremedchiev d_keremedchiev@bas.bg
% Todor Balabanov todorb@iinf.bas.bg

\date{}

\begin{document}

\maketitle

The educational system in Bulgaria covers twelve grades. The quality of the education is measured at the end of the academic year. Students take written exams in the fourth, seventh and twelfth grade. The evaluation of these exams is concerned with a lot of paper work and documents exchange. The results of the evaluation should be provided to the authorities in a secure and reliable way. With the modern blockchain a school-based distributed computing environment can be created and many of the current difficulties can be overcome. By design, a blockchain is resistant to data modification and provides security and data integrity. In order to create such a blockchain each school has to support a blockchain based peer in its IT infrastructure. The Ministry of Education will be able to access all relevant data in a convenient and secure way. The blockchain technology will prevent manipulation of  test results. Reliable information can be provided for interested institutions such as universities and potential employers. In this paper possibilities for blockchain implementation in schools which leads to improvement of  Bulgarian school educational system are discussed.

\end{document}
